---
title: "VISTA 2012-13 Activities"
author: "Dhirendra Singh"
output:
  pdf_document: default
  html_document:
    keep_md: no
urlcolor: blue
geometry: "left=1cm,right=1cm,top=3cm,bottom=3cm"
---

# About 
*This document was generated on `r as.character(format(Sys.Date(), format="%B %d, %Y"))`.*

```{r echo=FALSE}
suppressMessages(library(reshape2))
suppressMessages(library(ggplot2))
suppressMessages(library(plyr))
suppressMessages(library(dplyr))

vista_csv='vista_2012_13_dedjtr_activities.csv'
vista_data<-read.csv(vista_csv,header = T,sep=',',stringsAsFactors = F,strip.white = T)
```

# Input Data

The Victorian Integrated Survey of Travel & Activity (VISTA) 2012-13 table of activities by time of day for weekdays and weekend days is loaded from `r vista_csv`. The file was created by:

1. exporting the [VISTA 2012-13 Population Activity profile from DEDJTR](https://public.tableau.com/profile/dedjtr#!/vizhome/VISTA2012-13-Populationactivityprofile/PopulationActivityprofile) in Tableau format;
1. loading the downloaded data in Tableuau Public Desktop; and then
1. exporting the data from Tableau Public Desktop to CSV.

(The alternative would have been to directly process the VISTA data files (also CSVs), but that requires adjusting numbers by using the weights correctly, whereas the DEDJTR file already contains the adjusted numbers.)

A sample record showing the structure of the input data is given below. 

```{r echo=FALSE}
print( knitr::kable(t(head(vista_data,1)), col.names = c("")))
```

\newpage
# Data Processing

```{r echo=FALSE}
orig<-vista_data[,c("Purpose.S..group.","Population","Time1","Travdow..group.")]
colnames(orig)<-c("Purpose","Population","Time", "DayOfWeek")
orig$Hour<-as.numeric(lapply(orig$Time, function(y) 
  sapply(strsplit(y,":"), function(x) {
    x <- as.numeric(x)
    x[1]+x[2]/60
  })))
orig$Hour<-orig$Hour-min(orig$Hour)

week<-orig
week$Population[is.na(week$Population)] <- 0
week<-aggregate(week[c("Population")], by=week[c("Purpose","Hour","DayOfWeek")], sum)

# remove 24th hour which is conceptually doubling up with the 0th hour
week<-week[week$Hour<24,]

# remove **Travelling / accompanying** as it represents people in transit and not at location=-based activities
week<-week[week$Purpose!="Travelling / accompanying",]

# collapse data into 2hr blocks
week$HourRange<-cut(
  week$Hour, right=FALSE, 
  breaks=c(0,2,4,6,8,10,12,14,16,18,20,22,24),
  labels = c("0-2","2-4","4-6","6-8","8-10","10-12","12-14","14-16","16-18","18-20","20-22","22-24"))
week<-aggregate(week[c("Population")], by=week[c("Purpose","HourRange","DayOfWeek")], sum)

# each time slot should add up to 100% of the population but doesn't so must be adjusted

# use the largest value of population from any time bin to represent 100% of the population
total_popn<-max(aggregate(week[c("Population")], by=week[c("HourRange","DayOfWeek")], sum)$Population)
week$Percentage<-100*(week$Population/total_popn);
# now find out what percentage of the population is unaccounted for in each time bin
unknonwn<-100-aggregate(week[c("Percentage")], by=week[c("HourRange","DayOfWeek")], sum)$Percentage
# add the unknowns to the "Other / not stated" bucket to make each time bin 100%
week[week$Purpose=="Other / not stated",]$Percentage=week[week$Purpose=="Other / not stated",]$Percentage+unknonwn
week$Percentage<-round(week$Percentage,1)
```

Our intent is to create a *time-of-day distribution of activities for the aggregated Melbourne population (31 LGAs)* from VISTA data, as input for the [EES synthetic population generation algorithm](https://github.com/agentsoz/synthetic-population). We do this as follows:

1. Convert the hour of day (`Time1`) field to a decimal;
1. subtract `4.0` from the hour of day since the range in the input data is `[4.0,28.0]` when it should be `[0.0,24.0]`;
1. remove records for the 24th hour, which conceptually is the same as the 0th hour of day;
1. remove records for the `Purpose` category **Travelling / accompanying** as it represents people in transit and not at location-based activities;  
1. sum the time of day records into 2-hour time bins as required by the synthetic population generation algorithm;
1. ensure that each time bin includes 100% of the population; we do this by taking the largest value of `Population` from any time bin to represent 100% of the population,  calculating how much of the population is unaccounted for in each time bin (with respect to this number), and then adding the unaccounted to the `Purpose` category **Other / not stated**;
1. separate the data into two groups by categories **Weekdays** and **Weekend days**.

\newpage
# VISTA 2012-13 Weekday Activities by Time of Day


```{r echo=FALSE}
weekdays<-week[week$DayOfWeek=="Weekdays",c("Purpose", "HourRange", "Percentage")]
df<-weekdays
df<-aggregate(df[c("Percentage")], by=df[c("Purpose","HourRange")], sum)
d<-melt(df, id.vars=c("Purpose", "HourRange"))
ggplot(d, aes(HourRange,value, col=Purpose, fill=Purpose)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  geom_bar(stat="identity", color="black", size=0.1, position = "stack") +
  xlab("Hour of day") + ylab("Percentage of population") + 
  ggtitle(NULL)

table<-acast(weekdays, Purpose ~ HourRange, 
             function(x) {sort(as.character(x))[1]},
             value.var = 'Percentage', fill = '0')

rnames<-rownames(table)
rnames<-gsub("At Home", "home", rnames)
rnames<-gsub("Education", "education", rnames)
rnames<-gsub("Other / not stated", "other", rnames)
rnames<-gsub("Shopping", "shop", rnames)
rnames<-gsub("Social / Rec", "recreation", rnames)
rnames<-gsub("Work Related", "work", rnames)

table<-apply(table, 2, as.numeric)
rownames(table)<-rnames
write.csv(table, "vista_2012_13_activities_weekdays.csv", quote=FALSE)
print( knitr::kable(table))
```
\newpage
# VISTA 2012-13 Weekend Activities by Time of Day

```{r echo=FALSE}
weekends<-week[week$DayOfWeek=="Weekend days",c("Purpose", "HourRange", "Percentage")]
df<-weekends
df<-aggregate(df[c("Percentage")], by=df[c("Purpose","HourRange")], sum)
d<-melt(df, id.vars=c("Purpose", "HourRange"))
ggplot(d, aes(HourRange,value, col=Purpose, fill=Purpose)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  geom_bar(stat="identity", color="black", size=0.1, position = "stack") +
  xlab("Hour of day") + ylab("Percentage of population") + 
  ggtitle(NULL)

table<-acast(weekends, Purpose ~ HourRange, 
             function(x) {sort(as.character(x))[1]},
             value.var = 'Percentage', fill = '0')

rnames<-rownames(table)
rnames<-gsub("At Home", "home", rnames)
rnames<-gsub("Education", "education", rnames)
rnames<-gsub("Other / not stated", "other", rnames)
rnames<-gsub("Shopping", "shop", rnames)
rnames<-gsub("Social / Rec", "recreation", rnames)
rnames<-gsub("Work Related", "work", rnames)

table<-apply(table, 2, as.numeric)
rownames(table)<-rnames

write.csv(table, "vista_2012_13_activities_weekends.csv", quote=FALSE)
print( knitr::kable(table))

```


